Adaptive evolution with aneuploidy and mutation

### 2022-01-17 ms/ms.tex
update TODOs; fix affil

\affil[1]{School of Computer Sciences, Reichman University, Herzliya, Israel}
\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[3]{Institute of Biochemistry, Food Science and Nutrition,
Robert H. Smith Faculty of Agriculture, Food and Environment,
The Hebrew University of Jerusalem, Israel}
%\affil[d]{Department of Molecular Genetics, Weizmann Institute of Science, Rehovot 76100, Israel}
\affil[*]{These authors contributed equally to this work}
\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}

@@

%%%%%%%% Fig illustation
\begin{figure}[b!]
  %\centering
  \begin{subfigure}[t]{0.4\textwidth}
      \caption{
        \textbf{A. Single-locus model}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/Fig1-A.pdf}      
      \label{fig:model1}
  \end{subfigure}
  %\\
  \begin{subfigure}[t]{0.4\textwidth}
  	  \caption{
        \textbf{B. Multi-locus model}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/Fig1-B.pdf}      
      \label{fig:model2}
  \end{subfigure}
  \caption{
    \textbf{Model illustrations.}
    \textbf{(A)} In the single-locus model, the four genotypes are: euploid wild-type, \euwt; euploid mutant, \eumt; aneuploid wild-type, \anwt; and aneuploid mutant, \anmt.
    Overall there are two possible trajectories from \euwt\; to \eumt.
    \textbf{(B)} In the multi-locus model, each genotype is characterized by its karyotype, \euwt\; or \anwt, and the number of accumulated beneficial mutations, denoted by stars. 
    In both panels arrows denote transitions between genotypes, with transitions rates: $\mu$, beneficial mutation rate; $\delta$, aneuploidy rate.
    % TODO IK: remove k (not tau either!); also k mu is too close to the arrow right now; change alpha to delta in the figure 
  }
  \label{fig:models}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
  \centering
\includegraphics[width=0.8\textwidth]{../figures/ppc-plot.pdf}
  \caption{
  \textbf{Single-locus model posterior genotype frequency dynamics.} 
  The posterior predicted frequency of the four genotypes. Each curve is the average of 10,000 simulations using parameters drawn from the posterior distribution (\autoref{fig:posterior}).
  }
  \label{fig:ppc-plot}
  % TODO add legend
  % xticks - replace 500, 1000,1500,2000,2500 with 450, 1700, 2350
\end{figure}

>>>>

\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[3]{Institute of Biochemistry, Food Science and Nutrition,
Robert H. Smith Faculty of Agriculture, Food and Environment,
The Hebrew University of Jerusalem, Israel}
%\affil[d]{Department of Molecular Genetics, Weizmann Institute of Science, Rehovot 76100, Israel}
\affil[*]{These authors contributed equally to this work}
\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}

@@

%%%%%%%% Fig illustation
\begin{figure}[b!]
  %\centering
  \begin{subfigure}[t]{0.4\textwidth}
      \caption{
        \textbf{A. Single-locus model}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/Fig1-A.pdf}      
      \label{fig:model1}
  \end{subfigure}
  %\\
  \begin{subfigure}[t]{0.4\textwidth}
  	  \caption{
        \textbf{B. Multi-locus model}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/Fig1-B.pdf}      
      \label{fig:model2}
  \end{subfigure}
  \caption{
    \textbf{Model illustrations.}
    \textbf{(A)} In the single-locus model, the four genotypes are: euploid wild-type, \euwt; euploid mutant, \eumt; aneuploid wild-type, \anwt; and aneuploid mutant, \anmt.
    Overall there are two possible trajectories from \euwt\; to \eumt.
    \textbf{(B)} In the multi-locus model, each genotype is characterized by its karyotype, \euwt\; or \anwt, and the number of accumulated beneficial mutations, denoted by stars. 
    In both panels arrows denote transitions between genotypes, with transitions rates: $\mu$, beneficial mutation rate; $\delta$, aneuploidy rate.
  }
  \label{fig:models}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
  \centering
\includegraphics[width=0.8\textwidth]{../figures/dynamics.pdf}
  \caption{
  \textbf{Single-locus model posterior genotype frequency dynamics.} 
  The posterior predicted frequency of the four genotypes. Each of 20 curves is the average of 10,000 simulations using parameters drawn from the posterior distribution (\autoref{fig:posterior}).
  }
  \label{fig:ppc-plot}
  % TODO put legend inside figure - I think there is room in middle right
\end{figure}
